\documentclass[11pt,a4paper,oneside]{report}             % Single-side
%\documentclass[11pt,a4paper,twoside,openright]{report}  % Duplex

%\PassOptionsToPackage{chapternumber=Huordinal}{magyar.ldf}
\usepackage{t1enc}
\usepackage[latin2]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage[thmmarks]{ntheorem}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{listings}
\usepackage{color}
%\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{lastpage}
\usepackage{anysize}
\usepackage[magyar]{babel}
\usepackage{sectsty}
\usepackage{setspace}  % Ettol a tablazatok, abrak, labjegyzetek maradnak 1-es sorkozzel!
\usepackage[hang]{caption}
\usepackage[obeyspaces]{url}
\usepackage{hyperref}
\usepackage{floatrow}
\usepackage{indentfirst} % Ettõl a pontok elsõ bekezdése is behúzott lesz
\usepackage{multicol}
\usepackage{placeins}

%--------------------------------------------------------------------------------------
% Main variables
%--------------------------------------------------------------------------------------
\newcommand{\vikszerzo}{Halász Antal István}
\newcommand{\vikkonzulens}{Dr.~Toka László}
\newcommand{\vikcim}{Multi-platform sportkövetõ mobilalkalmazás tervezése és fejlesztése}
\newcommand{\viktanszek}{Távközlési és Médiainformatikai Tanszék}
\newcommand{\vikdoktipus}{Szakdolgozat}
\newcommand{\vikdepartmentr}{Bódis-Szomorú András}

%--------------------------------------------------------------------------------------
% Page layout setup
%--------------------------------------------------------------------------------------
% we need to redefine the pagestyle plain
% another possibility is to use the body of this command without \fancypagestyle
% and use \pagestyle{fancy} but in that case the special pages
% (like the ToC, the References, and the Chapter pages)remain in plane style

\pagestyle{plain}
%\setlength{\parindent}{0pt} % áttekinthetõbb, angol nyelvû dokumentumokban jellemzõ
%\setlength{\parskip}{8pt plus 3pt minus 3pt} % áttekinthetõbb, angol nyelvû dokumentumokban jellemzõ
\setlength{\parindent}{12pt} % magyar nyelvû dokumentumokban jellemzõ
\setlength{\parskip}{0pt}    % magyar nyelvû dokumentumokban jellemzõ

\marginsize{35mm}{25mm}{15mm}{15mm} % anysize package
\setcounter{secnumdepth}{0}
\sectionfont{\large\upshape\bfseries}
\setcounter{secnumdepth}{2}
\singlespacing
\frenchspacing

%--------------------------------------------------------------------------------------
%	Setup hyperref package
%--------------------------------------------------------------------------------------
\hypersetup{
    bookmarks=true,            % show bookmarks bar?
    unicode=false,             % non-Latin characters in Acrobat’s bookmarks
    pdftitle={\vikcim},        % title
    pdfauthor={\vikszerzo},    % author
    pdfsubject={\vikdoktipus}, % subject of the document
    pdfcreator={\vikszerzo},   % creator of the document
    pdfproducer={Producer},    % producer of the document
    pdfkeywords={keywords},    % list of keywords
    pdfnewwindow=true,         % links in new window
    colorlinks=true,           % false: boxed links; true: colored links
    linkcolor=black,           % color of internal links
    citecolor=black,           % color of links to bibliography
    filecolor=black,           % color of file links
    urlcolor=black             % color of external links
}

%--------------------------------------------------------------------------------------
% Set up listings
%--------------------------------------------------------------------------------------
\captionsetup[lstlisting]{position=bottom}
\lstset{
	basicstyle=\scriptsize\ttfamily, % print whole listing small
	keywordstyle=\color{black}\bfseries\underbar, % underlined bold black keywords
	identifierstyle=, 					% nothing happens
	commentstyle=\color{white}, % white comments
	stringstyle=\scriptsize\sffamily, 			% typewriter type for strings
	showstringspaces=false,     % no special string spaces
	aboveskip=3pt,
	belowskip=3pt,
	columns=fixed,
	backgroundcolor=\color{lightgray},
} 		
\def\lstlistingname{kódrészlet}

%--------------------------------------------------------------------------------------
%	Some new commands and declarations
%--------------------------------------------------------------------------------------
\newcommand{\code}[1]{{\upshape\ttfamily\scriptsize\indent #1}}
\newcommand{\Csharp}{C\texttt{\#}}
\newcommand{\CsharpDotNet}{C\texttt{\#/}.NET}
\def \screenShotWidth {63mm}
\def \appendicesScreenShotWidth {58mm}
\def \appendicesHSpaceLength {10mm}
\def \appendicesVSpaceLength {10mm}

\floatstyle{boxed}
\newfloat{program}{thpb}{aux}[chapter]
\floatname{program}{kódrészlet}	

% define references
\newcommand{\figref}[1]{\ref{fig:#1}.}
\renewcommand{\eqref}[1]{(\ref{eq:#1})}
\newcommand{\listref}[1]{\ref{listing:#1}.}
\newcommand{\sectref}[1]{\ref{sect:#1}}
\newcommand{\tabref}[1]{\ref{tab:#1}.}

\DeclareMathOperator*{\argmax}{arg\,max}
%\DeclareMathOperator*[1]{\floor}{arg\,max}
\DeclareMathOperator{\sign}{sgn}
\DeclareMathOperator{\rot}{rot}
\definecolor{lightgray}{rgb}{0.95,0.95,0.95}

\author{\vikszerzo}
\title{\viktitle}
%--------------------------------------------------------------------------------------
%	Setup captions
%--------------------------------------------------------------------------------------
\captionsetup[figure]{
%labelsep=none,
%font={footnotesize,it},
%justification=justified,
width=.75\textwidth,
aboveskip=10pt}

\renewcommand{\captionlabelfont}{\small\bf}
\renewcommand{\captionfont}{\footnotesize\it}

%--------------------------------------------------------------------------------------
% Table of contents and the main text
%--------------------------------------------------------------------------------------
\begin{document}
\singlespacing


\onehalfspacing

%----------------------------------------------------------------------------
% Abstract in hungarian
%----------------------------------------------------------------------------
\chapter*{Összefoglaló}

Napjainkra a komplex operációs rendszereket futtató, számos szenzorral és funkcionalitással rendelkezõ okostelefonok az átlagember mindennapjainak szerves részévé váltak.
A sport, mint kikapcsolódási forma egyre többeket vonz, melynek az okostelefon-használat is részévé vált.
Az emberek szeretnék teljesítményüket mérni, nyomon követni, valamint részletes statisztikák alapján sportolási tevékenységüket javítani, finomhangolni.

Amíg a jelenleg elérhetõ sportkövetõ mobilapplikációk kiválóan alkalmasak szabadtéri sportok analíziséhez, addig a beltéren végzett sportoknál kézzel kell felvinnie a felhasználónak edzése jellemzõit.

A tanszéki SmartActive projekt célja a squash sport lehetõségeit vizsgálva új elemeket vinni a játékba, illetve részletesebb statisztikákat nyújtani a játékosoknak teljesítményükrõl, kezdõtõl profi szintig.
A rendszer adatokat gyûjt a játék során, majd egy adatbázisban tárolja, amiket a felhasználók egy webportálon keresztül elérhetnek.
A projekt egy másik célja a felhasználók közti interakció megvalósítása, például bajnokságok szervezésének lehetõsége, amire a játékosok kihívhatják barátaikat.
A feladatom egy olyan multi-platform mobilalkalmazás fejlesztése volt, ami támogatja ezeket a funkciókat.

Szakdolgozatomban elõször ismertettem a készítendõ mobilalkalmazás koncepcióját.
Ezután megvizsgáltam a jelenleg elérhetõ multi-platform mobilszoftverfejlesztõ-\linebreak 
keretrendszereket, és értékeltem õket a megvalósítandó applikációhoz való alkalmasságuk szempontjából.
Bemutattam a Xamarin multi-platform keretrendszerben történõ fejlesztéshez szükséges eszközöket, azok beállítását és használatát.
A keretrendszer fejlesztési lehetõségeit megvizsgáltam, ismertettem az alkalmazás elkészítése során felhasznált fontosabb elemeit, valamint a hibákat, amikkel a fejlesztés során találkoztam.
Részleteztem az alkalmazás struktúráját, emellett kitértem az implementációhoz használt fõbb programozási paradigmákra és a unit tesztelésre.
Végül részletesen bemutattam az elkészült alkalmazás grafikus felületét és annak mûködését.
Az applikáció funkcionalitása és struktúrája minden célplatformon megegyezik, ezzel azonos élményt nyújtva a felhasználóknak.
\vfill
\thispagestyle{empty}
%----------------------------------------------------------------------------
% Abstract in english
%----------------------------------------------------------------------------
\chapter*{Abstract}

Smartphones, which run complex operating systems, are equipped with numerous sensors and provide a rich feature set, have become an integral part of our everyday lives.
Exercising as a free time activity is more and more appealing and smartphones are used in this area as well.
People would like to measure and track their progress, also improve and tune it based on detailed statistics about it.

While the currently available mobile applications are perfectly capable of tracking outdoor sports, indoor activity details have to be added manually to the app.
The main goal of the department's SmartActive project is to examine the possibilities of squash to add new elements to it, also to provide detailed and useful statistics for the players about their performance, at any scale from beginner to professional levels.
The system collects data during the gameplay, which is stored in a database that can be accessed through a web portal.
Another goal of the project is to provide a community platform to the users, e.g. someone can organize a tournament, to which he/she can invite his/her friends.
My objective was to design and develop a cross-platform mobile application, which can support these features.

In my bachelor thesis I first introduced the concept of the mobile application to be developed.
After that I examined the currently available cross platform mobile software development frameworks and reviewed them by their compatibility to the SmartActive mobile application.
Then I presented the needed tools for starting development in the Xamarin framework, also showed their correct settings and usage.
I reviewed the options of development in the framework, presented its main elements used for the development, also their issues, which I encountered while implementing the program.
I gave a detailed view of the mobile application's structure, also touched upon the main programming paradigms and unit testing concept I used for the implementation.
Finally, I presented the completed application's user interface and its operation in detail.
The structure and feature set of the program is the same on all target platforms, thus providing a consistent user experience.
\vfill
\thispagestyle{empty}
\label{page:last}
\end{document}
